### 2022-05-24 main/chapter_2ljets.tex
fix a sentence
move b tagging to where objects will be
first runthough trigger sec

A more precise frame problem with RJR variables is that they select phase space
which tends to be poorly modelled by simulations.
This is plausibly explained by the fact that  RJR variables are non-trivially
related to conventional, lab-frame variables.
Simulations have been tuned to model conventional variables well, and
`systematic' variations are evaluated and derived in conventional variables.
Not all functions of the data are well understood.
These effects cause Monte Carlo simulations to give predictions in RJR regions
which are inaccurate and/or carry large uncertainties.

@@

@@

\subsection{Stranverse mass $\mttwo$}
\label{sec:mt2}
% TODO
% angle between the vector sum of the lepton pair and the missing transverse momentum.
% leptons and the missing transverse momentum.
% If two massive particles are pair produced and each decays to a
% lepton and something massless and invisible,
% then this estimates a greatest lower bound on the invariant
% mass of the pair produced particles.
% $\mttwo(\ell, \ell; 0)$ is useful for excluding standard model backgrounds;
% di-leptonic ttbar ($tt\rightarrow WW\rightarrow\ell\nu\ell\nu$)
% and $WW\rightarrow\ell\nu\ell\nu$ have a kinematic endpoint
% at the $W$ pole mass, and $\tau\tau$ is constrained within measurement error of zero.

@@

\subsection{$b$-tagging}
\label{sec:btagging}
% with $\pt > 20$ GeV,
% where the tag is taken on the mv2c10 classifier at the $77\%$ working point.

>>>>

A more precisely framed problem with RJR variables is that they tend to select
phase space which is poorly modelled by simulations.
This is plausibly explained by the fact that  RJR variables are non-trivially
related to conventional, lab-frame variables.
Simulations have been tuned to model conventional variables well, and
`systematic' variations are evaluated and derived in conventional variables.
Not all functions of the data are well understood.
These effects cause Monte Carlo simulations to give predictions in RJR regions
which are inaccurate and/or carry large uncertainties.

@@

\subsection{Trigger}
There would be no event variables if not for the trigger.
When living our daily lives, we are bombarded with sensory data and must pay
attention only only those gems few of any use, to avoid exhausting our
processing capacity.
Running \atlas\ is no different.

Each trigger in \atlas' arsenal activates on a selection comprising some
combination of sufficiently hard objects.
The set of targeted objects includes all those used in this analysis and more:
electron, muons, jets, $b$-jets, $\met$, as well as photons and hadronically
decaying tau leptons~\cite{atlas_PERF_2007_01}.

The list of available triggers in \atlas\ is designed to balance data rates
against physical interest.
It includes a variety of general purpose selections, which are used for
$\twoljets$, along with more specialized targets such as vector boson fusion
or long lived particles.
The list varies through time, so we select triggers specifically in
each data-taking period.

The loosest triggers are `prescaled' --- their data rate is reduced by randomly
accepting only a small fraction of events.
For $\twoljets$, we use only the `lowest' (loosest, highest rate) un-prescaled
triggers selecting two charged leptons~\cite{atlas_twiki_lowest_unprescaled}.
Those charged leptons are selected in the
high-level trigger (described in Section~\ref{sec:atlas_trigger})
primarily requiring large $\pt$ and certain quality criteria which vary by
trigger.

In total, we use $14$ different two-lepton trigger selections, each of which
selects for an electron pair, a muon pair, or an emu (electron-muon pair).
To describe those triggers let $\pt^{\ell_i}$ be the transverse momentum of the
$i\mathrm{th}$ hardest lepton.

In short, all triggers require $\pt^{\ell_i}$ values to exceed
$8\textrm{--}26~\eV[G]$.
To detail all trigger requirements and their variations with data period
would be too tedious and not enlightening, but their $\pt^{\ell_i}$ requirements
are summarized here.
\begin{itemize}
\item Electron pair: requirements vary between
\begin{itemize}
\item $\pt^{e_2} > 12~\eV[G]$ and
\item $\pt^{e_2} > 17~\eV[G]$.
\end{itemize}
\item Muon pair: symmetric requirements vary between
\begin{itemize}
\item $\pt^{\mu_2} > 10~\eV[G]$ and
\item $\pt^{\mu_2} > 14~\eV[G]$.
\end{itemize}
Asymmetric requirements vary between
\begin{itemize}
\item $\pt^{\mu_1} > 18~\eV[G]~\&~\pt^{\mu_2} > 8~\eV[G]$, and
\item $\pt^{\mu_1} > 22~\eV[G]~\&~\pt^{\mu_2} > 8~\eV[G]$.
\end{itemize}
\item Emu pair: various asymmetric requirements include
\begin{itemize}
\item $\pt^{e_1} > 17~\eV[G]~\&~\pt^{\mu_1} > 14~\eV[G]$,
\item $\pt^{e_1} > 7~\eV[G]~\&~\pt^{\mu_1} > 24~\eV[G]$, and
\item $\pt^{e_1} > 26~\eV[G]~\&~\pt^{\mu_1} > 8~\eV[G]$.
\end{itemize}
\end{itemize}

\subsubsection{Alternative triggers}
\textit{Knut Vadla} \TODO

\subsection{Leptons}
Charged leptons are essential to the $\twoljets$ analysis.

\subsection{Jets}

\subsubsection{$b$-tagging}
\label{sec:btagging}

\subsection{$\met$}

@@

\subsection{Stranverse mass $\mttwo$}
\label{sec:mt2}

@@
